Data Exploration

### 2019-03-07 src/data_exploration.Rmd
stack predict loop done
arghhhhh!!!

# Package dependencies
You can load them using the following code which uses a function called [ipak](https://gist.github.com/stevenworthington/3178163). 
Note this function checks to see if the packages are installed first.
The "include=FALSE" supresses the package installation text appearing in the document...
```{r pre-install packages, include=FALSE}
packages <- c("plyr", "graphics", "ggplot2", "corrplot", "FSA", "car", "rworldmap", "fastmatch") 
source("../src/ipak.R")
ipak(packages)
```

@@

@@

```{r}
```{r}
system.file("java", package="dismo") #finding location to put maxent jar file
system("java -version")
```

>>>>

# Package dependencies
You can load them using the following code which uses a function called [ipak](https://gist.github.com/stevenworthington/3178163). 
Note this function checks to see if the packages are installed first.
The "include=FALSE" supresses the package installation text appearing in the document...
```{r pre-install packages, include=FALSE}
packages <- c("plyr", "graphics", "ggplot2", "corrplot", "FSA", "car", "rworldmap", "fastmatch", "tables") 
source("../src/ipak.R")
ipak(packages)
```

@@

and by year

```{r}
gearby_yr <- with(presence, table(gear, year))
write.csv(gearby_yr, file = "../output/bio/gear_by_yr.csv")
gearby_yr
```

@@
